\section{Introduction}

This document outlines the LaTeX Writing Standard, providing guidelines and best practices for creating well-structured and consistent LaTeX documents. The key elements covered in this document include:

\begin{itemize}
    \item \textbf{Document Structure and Organization:} Recommended directory layout and project initialization templates.
    \item \textbf{Core Preamble Configuration:} Essential packages, typography, layout settings, and metadata setup.
    \item \textbf{Common Environments and Code Snippets:} Guidelines for mathematical equations, tables, figures, and code listings.
    \item \textbf{Referencing and Bibliographies:} Instructions for bibliography management with BibTeX and citation examples.
    \item \textbf{Style Guidelines:} Consistent sectioning, macro definitions, and uniform formatting choices.
    \item \textbf{Version Control and Collaboration Standards:} Git integration, commit message conventions, and branching model.
    \item \textbf{Compilation and Build Process:} Preferred compiler and build instructions.
    \item \textbf{Quality Assurance and Checking Tools:} Linting and style checking tools, and CI integration.
    \item \textbf{Flexibility and Versioning of the Standard:} Core vs. add-on guidelines and update policy.
\end{itemize}

By following these guidelines, you can ensure that your LaTeX documents are consistent, well-organized, and maintainable.

For further details or for the full project, please visit the GitHub repository: \href{https://github.com/jerujj/latex_writing_standard}{\textbf{LaTeX writing standard repo}}

\end{document}